What We Eval in the Shadows

### 2021-08-09 paper/main.tex
Fix errors

\emph{Remove Boilerplate}

For example, the PopED::get_rse uses it to assign a number of variables in the current scope: eval(parse(text=paste(default_args[[i]]), "← ", i)). There are also more sophisticated cases. The plyr::allocate_column function uses eval for a deferred assignment to fill missing values in a column. Package overture repeatedly evaluates R expressions capturing any assignments that happen in it as samples of Markov chains.

\emph{Code Obfuscation} Some packages use \eval to bypass the restrictions
imposed by the \code{R CMD CHECK} tool. This tool enforces some well-formedness
rules on a submitted package before accepting it for inclusion in CRAN. Some
static checks ensure that the package code does not use certain restricted
functions. If package authors cannot avoid using these functions, they use \eval
to obfuscate the code, bypassing the checks performed by the tool. An example of
this use is the \code{scalaEnsure} function from the \code{aibd} package. It
mutates the variable \code{s} in the package environment. However, the package
environment in R is locked by default, which prevents bindings from being
mutated. Environment can be unlocked using \code{unlockBinding}, but its use is
flagged by the well-formedness checks. To work around this limitation, the
author passes the expression to unlock the package environment as a string to
\code{parse} which is then evaluated by \code{eval}.

@@

\emph{Miscellaneous}

>>>>

\emph{Avoid Boilerplate.}

For example, the \code{PopED::get\_rse} uses it to assign a number of variables
in the current scope: \code{eval(parse(text=paste(default_args[[i]]), "<- ",
  i))}. There are also more sophisticated cases. The \code{plyr::allocate\_column}
function uses eval for a deferred assignment to fill missing values in a column.
Package overture repeatedly evaluates R expressions capturing any assignments
that happen in it as samples of Markov chains.

\emph{Code Obfuscation.} Some packages use \eval to bypass the restrictions
imposed by the \code{R CMD CHECK} tool. This tool enforces some well-formedness
rules on a submitted package before accepting it for inclusion in CRAN. Some
static checks ensure that the package code does not use certain restricted
functions. If package authors cannot avoid using these functions, they use \eval
to obfuscate the code, bypassing the checks performed by the tool. An example of
this use is the \code{scalaEnsure} function from the \code{aibd} package. It
mutates the variable \code{s} in the package environment. However, the package
environment in R is locked by default, which prevents bindings from being
mutated. Environment can be unlocked using \code{unlockBinding}, but its use is
flagged by the well-formedness checks. To work around this limitation, the
author passes the expression to unlock the package environment as a string to
\code{parse} which is then evaluated by \code{eval}.

@@

\emph{Miscellaneous.}
